Title here

### 2020-06-23 paper/paper.Rmd
update

@@

>>>>

*In an optimization problem the goal is to find the best solution within the space of all feasible solutions which typically is represented by a set of constraints. The problem consists on optimizing an objective function $f: S \rightarrow \Re$ with $S \in \Re^n$ in a reduced spaced given by the problem constraints to either minimize or maximize a function.... Gradient based optimization has been typically used to solve such problems. However, there are many situations where derivatives of an objective function are unavailable or unreliable and therefore traditional methods based on derivatives are not the best option to solve an optimization problem....*

[Intro to optimization to set the scene for the paper? ppp]

@@

[How about adding more details into derivative free methods? ppp]
